\chapter{Technological frameworks}
\label{chap:techFrm}


% Provide a description of the technological frameworks used during the
% development phase of your product. Such technological frameworks
% should be properly introduced and described from the point of view of their
% use during the development of your product.
% 
% \section{Tool 1}
% \label{sec:Tool1}
% It was required to \ldots

\section{Java}
\label{sec:java}
Due to the need for developing software system some programming language should
be selected. Java has been chosen.


\section{Eclipse}
\label{sec:eclipse}
It was required to develop the system inside environment which supports
Java programmers in most part of their implementation issues (highlighting syntax
errors, project build, etc.). This environment should also be provided a on free
basis. Thus, the open-source Integrated Development Environment (IDE) for Java
programmers called Eclipse was chosen.

\section{MySQL}
\label{sec:mysql}
It was required to persistently store system's actors' information (information
about alerts, crises, etc.). Thus, some database engine should be chosen. MySQL
has been selected.

\section{MySQL Workbench}
\label{sec:mysqlworkbench}
It was required to find some database toolkit to conveniently and effectively
manage MySQL database engine. Thus, MySQL Workbench was selected.

\section{JavaFX}
\label{sec:javafx}
It was required to choose technological framework for GUI development. JavaFX
was chosen due to good separation of GUI and logic, and rich opportunities for
creating GUI.

\section{Scene Builder}
\label{sec:scenebuilder} 
It was required to find some tool to quickly define GUI layout with JavaFX.
Scene Builder was chosen.

\section{Remote Method Invocation (RMI)}
\label{sec:rmi}
It was required to determine protocol to be used for interaction between GUI
client and server. Remote Method Invocation (RMI) protocol was chosen, because
it is created exclusively for Java, provides good abstraction level (no
technological aspects of network communication such as in sockets, http) and has
well documented by Oracle company.
