\chapter{Introduction}
\label{chap:introduction}


\section{Overview}
The \mysystemname software system is intended to be used for secure crisis
handling and reporting.
The \mysystemname software system belongs to the Crisis Managment Systems
Domain. It is intended to be used for secure and convenient crisis reporting by
victim and witnesses (with a possibility to do so anonymously) and handling by
coordinators.



\section{Purpose and recipients of the document}
This document is a software design document, which is intended to describe and
summarize main decisions made about architecture and system design of
\mysystemname software system.

The audience of this document are employees of the development company (ADC),
who are responsible for \mysystemname software system production and
delivering. Document should be consulted during actual system implementation
and deployment and delivered software should meet all the decisions described in
the document.

\section{Definitions, acronyms and abbreviations}
All the terms required for proper document understanding: \\

\gls{MVC} a common design pattern followed to design the Graphical User
Interfaces in a consistent way.

\gls{Actor} An actor is a person, organization, or external system, which
interacts with a system.

\gls{system operation} system functionality, which could be inviked by an actor
passing a message.

\gls{Deployment View} describes components topology on a physical layer.

\gls{Implementation View} describes software system components layer.

\gls{UI Processing View} describes the interaction to a system, which allows
invocation of system operations.

\gls{abstract actor} an actor which could not have an inctance.

  
\section{Document structure} 
This document contains several chapters (sections), each of those describes
a \mysystemname design decisions from different points of view.

Chapter \ref{chap:introduction} contains document overview, description of the
document purpose and recipients and definitions, acronyms and abbreviations  used in a document.

Chapter \ref{chap:AM} provides decription of decision made during analysis
phase, in particular, software system types and system actors.

Chapter \ref{chap:techFrm} describes in detail technological frameworks used
 for \mysystemname production.

Chapter \ref{chap:arch} describes both hardware, required for \mysystemname
deployment and running, as well as behaviour of the software during the
 runtime.

Chapter \ref{chap:detDesign} in detail describes all system operations.

Chapter \ref{chap:know_limitations} lists all known problems of \mysystemname
and describes them in detail.

Chapter \ref{chap:final_conclusion} summarizes all the information retrieved
during design and implementation phase.
